---
title: "weather_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{weather_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Welcome to the vignette

Here you will get information about the functions

### First run this code

```{r setup}
library(weatherdata)
```

## About the Functions

### How to Use the `celsius_to_fahrenheit` Function

The **\``` celsius_to_fahrenheit()` ``** function converts temperatures from Celsius to Fahrenheit. This function accepts a numeric input representing the temperature in Celsius and returns the corresponding temperature in Fahrenheit.

#### Parameters:

-   **`temp_centigrados`**: A numeric value representing the temperature in Celsius that will be converted to Fahrenheit.

```{r}
celcius_to_fahrenheit(20)
```

### How to Use the `fahrenheit_to_celcius` Function

The \`**`` fahrenheit_to_celsius` ``**function converts temperatures from Fahrenheit to Celsius. This function accepts a numeric input representing the temperature in Fahrenheit and returns the corresponding temperature in Celsius.

#### Parameters:

-   **`temperature_fahrenheit`**: A numeric value representing the temperature in Fahrenheit that will be converted to Celsius.

```{r}
fahrenheit_to_celcius(50)
```

### How to Use the **`plot`** Function

The **`plot()`** function creates a bar plot that shows the average monthly temperature for a specified weather station over 40-year intervals. This visualization allows users to compare average temperatures across each month over different 40-year periods, providing a clear view of long-term temperature patterns for the station.

#### Parameters:

-   **`id`**: A character string that specifies the ID of the weather station for which the plot is to be generated. This ID should match one of the station IDs present in the `weatherdata` dataset to ensure accurate data retrieval.

```{r}
generate_40_year_average_temperature_plot("NH0472")
```

### How to Use the `download_and_read_weatherdata` Function

The `download_and_read_weatherdata()` function retrieves meteorological data from a set of predefined URLs, which correspond to different weather stations. After downloading the data, it combines these datasets into a single data frame for easier analysis and processing.

#### Parameters:

This function does not take any parameters, as it uses a predefined list of URLs to fetch data.


