---
title: "weather_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{weather_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  error = TRUE
)
```

## Welcome to the vignette

Here you will get information about the functions

### First run this code

```{r setup}
library(weatherdata)
```

## About the Functions

### How to Use the `celsius_to_fahrenheit` Function

The **\``` celsius_to_fahrenheit()` ``** function converts temperatures from Celsius to Fahrenheit. This function accepts a numeric input representing the temperature in Celsius and returns the corresponding temperature in Fahrenheit.

#### Parameters:

-   **`temp_centigrados`**: A numeric value representing the temperature in Celsius that will be converted to Fahrenheit.

```{r}
celcius_to_fahrenheit(20)
```

### How to Use the `fahrenheit_to_celcius` Function

The **`` fahrenheit_to_celsius` ``**function converts temperatures from Fahrenheit to Celsius. This function accepts a numeric input representing the temperature in Fahrenheit and returns the corresponding temperature in Celsius.

#### Parameters:

-   **`temperature_fahrenheit`**: A numeric value representing the temperature in Fahrenheit that will be converted to Celsius.

```{r}
fahrenheit_to_celcius(50)
```

### How to Use the **`get_meteorological_summary`** Function

The **`get_meteorological_summary()`** function calculates and returns key meteorological statistics for a specified weather station identified by its unique id. It provides the mean temperature, maximum temperature, minimum temperature, and average relative humidity for the given station. The function filters the dataset based on the provided id, computes these summary values, and returns them in a named numeric vector. If no data is found for the provided id, an error is raised to notify the user. This function is useful for quickly obtaining important meteorological information for analysis or reporting purposes.

#### Parameters:

-   **`id`**: A character string that specifies the ID of the weather station for which the plot is to be generated. This ID should match one of the station IDs present in the `weatherdata` dataset to ensure accurate data retrieval.

```{r}
get_meteorological_summary("NH0046")
```

### How to Use the `download_and_read_weatherdata` Function

The `download_and_read_weatherdata()` function retrieves meteorological data from a set of predefined URLs, which correspond to different weather stations. After downloading the data, it combines these datasets into a single data frame for easier analysis and processing.

#### Parameters:

This function does not take any parameters, as it uses a predefined list of URLs to fetch data.


